---
title: "R Coding Exercise"
output:
  html_document:
    toc: FALSE
---

Loading packages

```{r, warning=FALSE}
library(tidyverse) 
library("dslabs")
```

Loading data

```{r}
help(gapminder)
data("gapminder")
summary(gapminder)
class(gapminder)
head(gapminder)
```

Subsetting data from African countries

```{r}
africadata <- gapminder %>% 
  filter(continent=="Africa")

str(africadata)
summary(africadata)
```

Creating new objects from 'africadata'-- 'imle' containing infant mortality and life expectancy, and 'ple' containing population size and life expectancy

```{r}
imle <- africadata %>% 
  select(c(infant_mortality, life_expectancy))

str(imle)
summary(imle)

ple <- africadata %>% 
  select(c(population, life_expectancy))

str(ple)
summary(ple)

```

Data Visualization

```{r}
#| warning: false
#| fig-cap: "Infant Mortality Rate and Life Expectancy in African Countries -- 1960 - 2015"
imle %>% ggplot(aes(x=infant_mortality, y=life_expectancy)) + 
  geom_point() + labs(x = "Infant Mortality (per 1,000 births)", y = "Life Expectancy (years)")
```

```{r}
ple %>% ggplot(aes(x= log(population), y = life_expectancy)) + 
geom_point() + labs(x="Log Population", y = "Life Expectancy (years)")
```

Next, let's find out which years are missing data on infant mortality

```{r}
with(subset(africadata, is.na(infant_mortality)), year)
```

Subsetting data from the year 2000

```{r}
africa2000 <- africadata %>% 
  filter(year == "2000")

str(africa2000)
summary(africa2000)
```

Plotting data from African Countries in 2000

```{r}
africa2000 %>% ggplot(aes(x=infant_mortality, y=life_expectancy)) +
geom_point() + labs(x = "Infant Mortality (per 1,000 births)", y = "Life
Expectancy (years)", title = "Infant Mortality Rate and Life Expectancy
in African Countries -- 2000")

africa2000 %>%  ggplot(aes(x= log(population), y = life_expectancy)) +
geom_point() + labs(x="Log Population", y = "Life Expectancy (years)",
title = "Population Size and Life Expectancy in African Countries --
2000")
```

Fitting a simple model

```{r}
fit1<-lm(life_expectancy ~ infant_mortality, data = africa2000)
fit2<-lm(life_expectancy ~ population, data = africa2000)
```

```{r}
summary(fit1) 
summary(fit2)
```

Conclusions

There is statistically significant evidence supporting an association between life expectancy and infant mortality. Life expectancy decreases by 2.49 years for every unit increase in infant mortality (p \< 0.05). The data does not show statistically significant evidence of association between life expectancy and population size (p = 0.62).

# New Section

This section has been added by Kailin (Kai) Chen.

## Continued Data Visualization and Analysis

### Country Contributions to Continental GDP

```{r}
# How Much Does Each Country Contribute to Continent's Overall GDP?
## Setting Up Initial Data
region_and_gdp <- africadata %>% filter(year == 1983) %>% group_by(region, gdp) %>% 
  select(country, region, gdp)
## Creating a New Variable for Continent's GDP
region_and_gdp$total_gdp <- sum(region_and_gdp$gdp, na.rm = TRUE)
# Percentage Contributed to Each 
region_and_gdp <- region_and_gdp %>%
  mutate(percentage = gdp/total_gdp * 100)

# Graphing African Countries' Contributions to Continent's GDP
ggplot(region_and_gdp, aes(x = percentage, y = country, group = region, fill = region)) + geom_col() + labs(x = "Percentage Contributed to Continent's GDP", y = "Nation", title = "Each Nation's Contribution to Continent's GDP in 1983")

```

### Looking at What Factors Affect Population in Asia

```{r}
library(broom)
# Creating a Model
population_factors_model <- lm(population ~ fertility + life_expectancy + infant_mortality, data = gapminder %>% filter(continent == "Asia"))

# Evaluating Model
pop_factors_model_table <- tidy(summary(population_factors_model))
```

According to this model, fertility (p \< 0.001) and life expectancy (p \< 0.001) appear to significantly impact population in Asia since the null hypothesis that they do not *is* rejected. However, the null hypothesis that infant mortality does not affect population, in contrast, *isn't* rejected.

## Fertility Over Time in Europe
```{r}
# Investigating Fertility Across Time
ggplot(gapminder %>% filter(continent == "Europe"), aes(x = year, y = fertility, group = region, color = region)) + geom_point() + labs(x = "Year", y = "Fertility Rate", title = "Fertility Over Time in Europe")
```
## Tracking Australia's GDP Over Time
```{r}
# Investigating Australia's GDP Across Time
ggplot(gapminder %>% filter(country == "Australia"), aes(x = year, y = gdp, color = year)) + geom_point() + geom_line() + labs(x = "Year", y = "GDP", title = "GDP Over Time for Australia")
```

