---
title: "Data Analysis Exercise"
output:
  html_document:
    toc: FALSE
---


This dataset describes drug poisoning deaths in the United States from 1999 - 2015 by demographic factors, including age group, sex, and a simple race/ethnicity variable (NH White, NH Black, Hispanic). This dataset includes all drug poisoning deaths-- intentional(suicide and homicide), unintentional, and those with undetermined intent. While this dataset includes some data at the state-level, further investigation into trends of drug poisoning deaths at the state level is limited due to the fact that the data have been aggregated. 

Let's load the packages we'll be using in this analysis.
```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(lubridate)
```

Loading the dataset...
```{r message=FALSE}
df <- read_csv("dataanalysis_exercise/rawdata/NCHS_-_Drug_Poisoning_Mortality_by_State__United_States.csv")
```

Let's take a look at the data.
```{r}
glimpse(df)
```

Let's remove observations at the state-level by filtering for only observations where 'state' is the "United States" and remove columns that we won't be using in the analysis.
```{r}
df <- df %>%  filter(State == "United States") %>% 
  select(!c(9:18)) %>% 
  select(!State)
```

Next, let's reclass some of our variables. We will also reorder the dataset so that Year is sorted chronologically, then by age group and sex.
```{r}
df <- df %>% 
  mutate(Age = factor(Age, level = (c("Less than 15 years", "15-24 years", "25-34 years",  "35-44 years", "45-54 years", "55-64 years", "65-74 years", "75+ years", "All Ages")))) %>% 
  mutate(Sex = as.factor(Sex)) %>% 
  mutate(`Race and Hispanic Origin` =  as.factor(`Race and Hispanic Origin`)) %>% 
  arrange(Year, Age, Sex)
```

Next, let's remove observations where rates have been aggregated and remove the columns with NA's, 
```{r}
df <- df %>% filter(!Age == "All Ages") %>% 
  filter(!Sex == "Both Sexes")

glimpse(df)
```

To make some of these variable easier to work with, let's rename them. 
```{r}
df <- df %>% 
  rename(race_eth = `Race and Hispanic Origin`) %>% 
  rename(crude_dr = `Crude Death Rate`)       
```

Let's see if we can extract some data from other minorities....
```{r}
all <- df %>% filter(race_eth == "All Races-All Origins")
nhw <- df %>% filter(race_eth == "Non-Hispanic White")
nhb <- df %>% filter(race_eth == "Non-Hispanic Black")
his <- df %>% filter(race_eth == "Hispanic")

all$Other_Deaths <- all$Deaths - nhw$Deaths - nhb$Deaths - his$Deaths
all$Other_Population <- all$Population - nhw$Population - nhb$Population - his$Population
all$Other_crude_dr <- (all$Other_Deaths/all$Other_Population) * 100000
all$Other_crude_dr <-  round(all$Other_crude_dr, 1)

other <- all %>%  select(Year, Sex, Age, Other_Deaths, Other_Population, Other_crude_dr)

other <- other %>% mutate(race_eth = "Non-Hispanic Other Race") %>% 
  rename(Deaths = Other_Deaths) %>% 
  rename(Population = Other_Population) %>% 
  rename(crude_dr = Other_crude_dr)

new_df <- full_join(nhb,nhw)
new_df <- full_join(new_df, his)
new_df <- full_join(new_df, other)

```

Before starting data visualization, let's reorder the race/ethnicity variable by decreasing crude death rate so that our legend for our plots is easier to interpret.
```{r}
new_df <- new_df %>% 
  mutate(race_eth = fct_reorder(race_eth, -crude_dr)) 
```

```{r}
saveRDS(new_df, "dataanalysis_exercise/processeddata/exercise4.rds")
```

Let's clear the environment and start fresh by loading up the RDS file we just saved!
```{r message = F}
rm(list = ls())

df <- readRDS("dataanalysis_exercise/processeddata/exercise4.rds")
```

Summary Table
```{r}
knitr::kable(df)
```

Data Visualization and next steps...
```{r message=FALSE}
df %>%  ggplot(aes(x= Year, y = crude_dr, color = race_eth)) + geom_smooth(se = F) + labs(title = "Trends in Drug Poisoning Death Rates by Race/ Ethnicity,
United States, 1999-2015", y = "Crude Death Rate (per 100,000)", x = "Year of Death", color = "Race/ Ethnicity")  + theme(legend.position="bottom") + guides(color=guide_legend(nrow=1,byrow=T)) +  theme(legend.title.align = 0.5, legend.direction = "vertical", legend.box.just = "center") + theme(plot.title = element_text(hjust = 0.5, size = 12))
```

My idea with this dataset is to explore trends in drug poisoning deaths across a number of demographic factors... 