---
title: "Tidy Tuesday Exercise 2"
output: 
  html_document:
    toc: FALSE
---
Let's load the data and other packages. We'll use the tidytuesdayR package to do this. 
```{r}
library(tidyverse)
library(lubridate)
library(tidymodels)
library(tidytuesdayR)
tuesdata <- tidytuesdayR::tt_load('2023-04-11')

eggproduction <- tuesdata$`egg-production`
cagefreepercentages <- tuesdata$`cage-free-percentages`
```

I've copied the following data dictionary from the TiduTuesday GitHub to reference more easily. 

### Data Dictionary

# `egg-production.csv`

|variable       |class     |description    |
|:--------------|:---------|:--------------|
|observed_month |double    |Month in which report observations are collected,Dates are recorded in ISO 8601 format YYYY-MM-DD |
|prod_type      |character |type of egg product: hatching, table eggs      |
|prod_process   |character |type of production process and housing: cage-free (organic), cage-free (non-organic), all. The value 'all' includes cage-free and conventional housing.   |
|n_hens         |double    |number of eggs produced by hens for a given month-type-process combo   |
|n_eggs         |double    |number of hens producing eggs for a given month-type-process combo     |
|source         |character |Original USDA report from which data are sourced. Values correspond to titles of PDF reports. Date of report is included in title.   |


# `cage-free-percentages.csv`

|variable       |class     |description    |
|:--------------|:---------|:--------------|
|observed_month |double    |Month in which report observations are collected,Dates are recorded in ISO 8601 format YYYY-MM-DD |
|percent_hens   |double    |observed or computed percentage of cage-free hens relative to all table-egg-laying hens  |
|percent_eggs   |double    |computed percentage of cage-free eggs relative to all table eggs,This variable is not available for data sourced from the Egg Markets Overview report |
|source         |character |Original USDA report from which data are sourced. Values correspond to titles of PDF reports. Date of report is included in title.  |



Let's start be taking a look at the data
```{r}
glimpse(eggproduction)
glimpse(cagefreepercentages)
```

It seems like these datasets span a different range of years. Let's verify this.
```{r}
eggproduction %>% 
  arrange(observed_month) %>%
  slice(c(1, n())) %>%
  bind_rows()

cagefreepercentages %>% 
  arrange(observed_month) %>%
  slice(c(1, n())) %>%
  bind_rows()
```

Let's prepare the datasets for a merge, which will hopefully this will make things easy to work with. I'll start by making a variable that pulls just the month and year from 'observed_month' to make merge the datasets more seamless.
```{r}
cagefreepercentages <- cagefreepercentages %>% 
  mutate(mon_yr = format_ISO8601(observed_month, precision = "ym"))

eggproduction <- eggproduction %>% 
  mutate(mon_yr = format_ISO8601(observed_month, precision = "ym"))
```

I'll do a bit more tidying up by using the computed estimates and by removing unnecessary variables
```{r}
cagefreepercentages_clean <- cagefreepercentages %>% 
  filter(source == "computed")%>% 
  select(-c(observed_month, source))

eggproduction_clean <- eggproduction %>% 
  select(-c(observed_month, source))
```

Now, we'll use inner join to merge by the mon_yr only that appear in both datasets
```{r}
eggs_df <- inner_join(eggproduction_clean, cagefreepercentages_clean, by = join_by(mon_yr))

eggs_df <- eggs_df %>% 
  mutate(prod_type = as.factor(prod_type),
         prod_process = as.factor(prod_process))

eggs_df$prod_type <- relevel(eggs_df$prod_type, ref = "table eggs")

eggs_clean <- eggs_df %>% select(-mon_yr)
```

```{r}
eggs_df <- eggs_df %>%
  mutate(all_cagefree = case_when(prod_process == "all" ~ "No",
                                          TRUE ~ "Yes"))



```

Let's split the data into test and train
```{r}
## setting the seed 
set.seed(123)
## Put 3/4 of the data into the training set 
data_split <- initial_split(eggs_clean, prop = 3/4)

# Create data frames for the two sets:
train_data <- training(data_split)
test_data <- testing(data_split)
```

Cross validation
```{r}
set.seed(123)
five_fold <- vfold_cv(train_data, v = 5)
```

Set the recipe
```{r}
eggs_rec <- recipe(n_eggs ~ ., data = train_data) %>% 
  step_dummy(prod_type, prod_process)
```

Now let's set up a null model
```{r}
null_mod <- null_model() %>% 
  set_engine("parsnip") %>% 
  set_mode("regression")
```

Null workflow
```{r}
null_wflow <- workflow() %>%
  add_model(null_mod) %>%
  add_recipe(eggs_rec)
```

```{r}
null_fit <- null_wflow %>% 
  fit(data = train_data)

null_fit %>%
  extract_fit_parsnip() %>%
  tidy()

fit_resamples(null_wflow, resamples = five_fold) %>%
  collect_metrics()
```

```{r}
null_aug <- augment(null_fit, train_data) 

null_aug %>% 
  select(n_eggs, .pred) %>%
  rmse(n_eggs, .pred)
```

Decision Tree
```{r}
library(rpart)

tune_spec <- 
  decision_tree(
    cost_complexity = tune(),
    tree_depth = tune()) %>% 
  set_engine("rpart") %>% 
  set_mode("regression")

tree_grid <- grid_regular(cost_complexity(),
                          tree_depth(),
                          levels = 5)
```

```{r warning=FALSE}
## workflow for decision tree
tree_wf <- workflow() %>%
  add_model(tune_spec) %>%
  add_recipe(eggs_rec)

tree_res <- 
  tree_wf %>% 
  tune_grid(resamples = five_fold,
    grid = tree_grid)
```

```{r}
tree_res %>% 
  collect_metrics() 

#visualize
tree_res %>%
  autoplot()

#Selecting the best tree using rmse.
best_tree <- tree_res %>%
  select_best(metric = "rmse") 

tree_ff_wf <- tree_wf %>% 
  finalize_workflow(best_tree)

tree_ff_wf %>% 
  fit(train_data)
```

#Lasso
```{r}
lasso_spec <- linear_reg(penalty = 0.1, mixture = 1) %>%
  set_engine("glmnet")

#Setting work flow
eggs_wflow <- workflow() %>%
  add_recipe(eggs_rec)

eggs_lasso_fit <- eggs_wflow %>%
  add_model(lasso_spec) %>%
  fit(data = train_data)

eggs_lasso_fit %>%
  pull_workflow_fit() %>%
  tidy()
```

```{r}
##Tune Lasso parameters
tune_spec <- linear_reg(penalty = tune(), mixture = 1) %>%
  set_engine("glmnet")

lambda_grid <- grid_regular(penalty(), levels = 50)
```

```{r}
# tune the grid using our workflow object.
doParallel::registerDoParallel()

set.seed(2020)
lasso_grid <- tune_grid(
  eggs_wflow %>% add_model(tune_spec),
  resamples = five_fold,
  grid = lambda_grid)
```

Let take a look at the results

```{r}
lasso_grid %>%
  collect_metrics()

lasso_grid %>% 
  autoplot
```

```{r}
#Let's find the parameter with the lowest rmse
lowest_rmse <- lasso_grid %>%
  select_best("rmse")

final_lasso_wf <- finalize_workflow(
  eggs_wflow %>% add_model(tune_spec),
  lowest_rmse)
```

```{r}
lasso_ff <- final_lasso_wf %>%
  fit(train_data)
lasso_ff 
```

```{r}
##Let look at the most important predictors
library(vip)

lasso_ff %>%
  pull_workflow_fit() %>%
  vi(lambda = lowest_rmse$penalty) %>%
  mutate(
    Importance = abs(Importance),
    Variable = fct_reorder(Variable, Importance)
  ) %>%
  ggplot(aes(x = Importance, y = Variable, fill = Sign)) +
  geom_col() +
  scale_x_continuous(expand = c(0, 0)) +
  labs(y = NULL)
```
Hatchling eggs have a negative association with the number of eggs produced.

##Random forest model
```{r}
rf_spec <- rand_forest(min_n = tune(),  
                       trees = 1000) %>%
  set_engine("ranger") %>%
  set_mode("regression")
```

Create tuning workflow for random forest model
```{r}
tune_wf <- workflow() %>%
  add_recipe(eggs_rec) %>%
  add_model(rf_spec)
```

```{r}
doParallel::registerDoParallel()

set.seed(345)
tune_res <- tune_grid(
  tune_wf,
  resamples = five_fold,
  grid = 20)

#Visualize..
tune_res %>% 
  autoplot()
```

```{r}
best_rf <- tune_res %>% 
  select_best(metric = "rmse")

rf_final_wf <- tune_wf %>%
  finalize_workflow(best_rf)

rf_final_wf %>% 
  fit(data = train_data)
```

Fitting the last model to testing data
```{r}
set.seed(345)
rf_final_fit <-
  rf_final_wf %>%
  last_fit(data_split)

rf_final_fit %>% 
  collect_metrics()
```

Multinomial regression via nnet
```{r}
# Specify a multinomial regression via nnet
multireg_spec <- multinom_reg(penalty = 1) %>% 
  set_engine("nnet") %>% 
  set_mode("classification")

# Train a multinomial regression model without any preprocessing
set.seed(2056)
multireg_fit <- multireg_spec %>% 
  fit(prod_type ~ ., data = train_data)

# Print the model
multireg_fit
```

```{r}
# Make predictions for the test set
eggs_results <- test_data %>%
  select(prod_type) %>% 
  bind_cols(multireg_fit %>% 
              predict(new_data = test_data)) %>% 
  bind_cols(multireg_fit %>% 
              predict(new_data = test_data, type = "prob"))
```