---
title: "Exploration"
editor: visual
---

```{r warning =FALSE, message = FALSE}
library(here)
library(tidyverse)
```

```{r}
flu <- readRDS(here("fluanalysis/data/processed_data/flu.rds"))
```

Let's take a look at some summary statistics for BodyTemp and Nausea

```{r}
summary(flu$BodyTemp)
summary(flu$Nausea)
```

Next, let's take a look at this distribution of BodyTemp.

```{r}
flu  %>% ggplot(aes(x = BodyTemp))  + geom_histogram(bins = 20)
```

I'm also interested in the intensity variables... Let's make a box plot of a couple of these with BodyTemp.

```{r}
flu %>% ggplot(aes(x= BodyTemp, y = Myalgia, color = Myalgia)) +
  geom_boxplot() 

flu %>% ggplot(aes(x= BodyTemp, y = Weakness, color = Weakness)) +
  geom_boxplot()
```

Median body temperature appears to increase with increasing intensity of myalgia/ weakness.

Let's look at this as a histogram for weakness.
```{r}
flu  %>% ggplot(aes(x = BodyTemp, fill = Weakness)) + 
  geom_histogram(bins = 20) 
```

Weakness by Nausea contingency table
```{r}
table(flu$Weakness,flu$Nausea)
```

Myalgia by Nausea contingency table
```{r}
table(flu$Myalgia,flu$Nausea)
```

Cough Intensity by Nausea contingency table
```{r}
table(flu$CoughIntensity,flu$Nausea)
```

Now let's take visualize this.
```{r warning= FALSE}
flu %>% ggplot(aes(x= Weakness, fill = CoughIntensity)) +
  geom_histogram(stat="count")

flu %>% ggplot(aes(x= Weakness, fill = Myalgia)) +
  geom_histogram(stat="count")

flu %>% ggplot(aes(x= Weakness, fill = Nausea)) +
  geom_histogram(stat="count")

```

Weakness by Nausea contingency table
```{r}
table(flu$Weakness,flu$Myalgia)
```