---
title: "Model fitting"
---

```{r warning=FALSE, message=FALSE}
library(here)
library(tidymodels)
library(performance)
library(tidyverse)
```

```{r}
flu <- readRDS(here("fluanalysis/data/processed_data/flu.rds"))
```

Univariate model for
```{r}
lm_mod <- linear_reg() %>% 
  set_engine("lm") %>% 
  fit(BodyTemp ~ Weakness, data = flu)

tidy(lm_mod)

glance(lm_mod)
```

Multivariate model (full)
```{r}
lm_full <- linear_reg() %>%
  set_engine("lm") %>% 
  fit(BodyTemp ~ . ,data = flu)

tidy(lm_full)
glance(lm_full)
```

Comparing model performance for univariate vs multivariate linear model.
```{r warning=FALSE}
compare_performance(lm_mod, lm_full)
```
The full model appears to be a better fit than univariate model with a lower AIC of 2307.8 and higher R2(adj.) of 0.086.

Let's try to make some predictions for the full model. We'll use the mean body temperature we found earlier
```{r}
new_points <- expand.grid(BodyTemp = 98.94, 
                          Weakness = c("None", "Mild", "Moderate", "Severe"))

##Mean prediction
mean_pred <- predict(lm_mod, new_data = new_points)
mean_pred

#Confidence intervals
conf_int_pred <- predict(lm_mod, 
                         new_data = new_points, 
                         type = "conf_int")
conf_int_pred
```

```{r}
plot_data <- 
  new_points %>% 
  bind_cols(mean_pred) %>% 
  bind_cols(conf_int_pred)

ggplot(plot_data, aes(x = Weakness)) + 
  geom_point(aes(y = .pred)) + 
  geom_errorbar(aes(ymin = .pred_lower, 
                    ymax = .pred_upper),
                width = .2) + 
  labs(y = "Body Temperature (F)")
```


Fitting univariate model - Logistic regression
```{r}
log_mod <- logistic_reg() %>% 
  set_engine("glm") %>% 
  fit(Nausea ~ Myalgia, data = flu)

tidy(log_mod)

#Results
glance(log_mod)
```
Fitting the full model - logistic regression
```{r}
log_full <- logistic_reg() %>% 
  set_engine("glm") %>% 
  fit(Nausea ~ ., data = flu)

tidy(log_full)
glance(log_full)
```

Comparing model performance for univariate vs multiple logistic regression model.
```{r warning=FALSE}
compare_performance(log_mod, log_full)
```
The full model appears to be a better fit than the univariate model, with an lower AIC of 821.5.