---
title: "Model Evaluation"
editor: visual
---

```{r warning =FALSE, message = FALSE}
library(here)
library(tidyverse)
library(tidymodels)
```

```{r}
flu <- readRDS(here("fluanalysis/data/processed_data/flu.rds"))
```

```{r}
# setting the seed 
set.seed(222)
# Put 3/4 of the data into the training set 
data_split <- initial_split(flu, prop = 3/4)

# Create data frames for the two sets:
train_data <- training(data_split)
test_data  <- testing(data_split)
```

```{r}
n_flu <- 
  recipe(Nausea ~ ., data = train_data) 
```

Setting logistic regression engine
```{r}
lr_mod <- 
  logistic_reg() %>% 
  set_engine("glm")
```

Creating workflow function using logistic regression model and training data
```{r}
flu_wflow <- 
  workflow() %>% 
  add_model(lr_mod) %>% 
  add_recipe(n_flu)
```

Creating function that can be used to prepare the recipe and train the model
```{r}
flu_fit <- 
  flu_wflow %>% 
  fit(data = train_data)
```

Extracting the model objects from the workflow
```{r}
flu_fit %>% 
  extract_fit_parsnip() %>% 
  tidy()
```
Usiing trained workflow to make predictions on testing data
```{r}
predict(flu_fit, test_data)

flu_aug <- 
  augment(flu_fit, test_data)

# The data look like: 
flu_aug %>%
  select(Nausea, .pred_No, .pred_Yes)
```
Plotting ROC_AUC
```{r}
flu_aug %>% 
  roc_curve(truth = Nausea, .pred_No) %>% 
  autoplot()

flu_aug %>% 
  roc_auc(truth = Nausea, .pred_No) 
```

Alternative model
```{r}
flu_r <- 
  recipe(Nausea ~ BodyTemp, data = train_data) 
```

Creating workflow function using lr model function and training data
```{r}
flu_wflow_r <- 
  workflow() %>% 
  add_model(lr_mod) %>% 
  add_recipe(flu_r)
```

Creating function that can be used to prepare the recipe and train the model
```{r}
flu_fit_r <- 
  flu_wflow_r %>% 
  fit(data = train_data)
```

Extracting the model objects from the workflow
```{r}
flu_fit_r %>% 
  extract_fit_parsnip() %>% 
  tidy()
```

Using trained workflow to make predictions on testing data
```{r}
predict(flu_fit_r, test_data)

flu_aug_r <- 
  augment(flu_fit_r, test_data)

# The data look like: 
flu_aug_r %>%
  select(Nausea, .pred_No, .pred_Yes)
```
Plotting ROC_AUC
```{r}
flu_aug_r %>% 
  roc_curve(truth = Nausea, .pred_No) %>% 
  autoplot()

flu_aug_r %>% 
  roc_auc(truth = Nausea, .pred_No) 
```
The model using only body temperature as a predictor performed much more poorly than the full model!
